Big Brother Is Watching

### 2015-11-05 manuscript.tex
bldlfksflksd
Conclusion touchup

\section{Conclusion}
\label{sec:conclusion}
In conclusion, both the Block Model and the Optimal Path model seem to agree on the fact that one would need at least 50 drones to optimally cover Manhattan/Gotham City. Unfortunately, those drones have infinite fuel, therefore the true solution needs to be adjusted according to the ratio of the drones' flight time to their recharge time; but this can be done without changing the strategy itself, just the timing of the drones' deployment. If we wanted to assuage the fears of some of the troublemakers, then we we would need at least 75 drones to properly cover 90\% of Manhattan. Thankfully, given that this is Gotham City, 75 to 100 drones seems quite cheap. One thing that we did not take into account is the fact that close to 100 years from now, Manhattan's east side will suffer from a little flooding, therefore our representation of Manhattan may not quite be spot on. Similarly, some avenues, like Broadway, which cut across Manhattan diagonally were not modeled by this. A more rigorous strategy would also try to include these types of streets, and would certainly include the fact that the number of jaywalkers varies with the time of day. For example, there will be very few jaywalkers in the Financial District near 3a.m., while there will be quite a few more during lunchtime.

>>>>

\section{Conclusion}
\label{sec:conclusion}
\par In conclusion, both the Block Model and the Optimal Path model seem to agree on the fact that one would need at least 50 drones to optimally cover Manhattan/Gotham City. Unfortunately, those drones have infinite fuel, therefore the true solution needs to be adjusted according to the ratio of the drones' flight time to their recharge time; but this can be done without changing the strategy itself, just the timing of the drones' deployment. If we wanted to assuage the fears of some of the troublemakers, then we we would need at least 75 drones to properly cover 90\% of Manhattan. Thankfully, given that this is Gotham City, 50 to 100 drones seems quite cheap.
\par One thing that we did not take into account is the fact that close to 100 years from now, Manhattan's east side will suffer from a little flooding, therefore our representation of Manhattan may not quite be spot on. Similarly, some avenues, like Broadway, which cut across Manhattan diagonally were not modeled. A more rigorous strategy would also try to include these types of streets, and would certainly include the fact that the number of jaywalkers varies with the time of day. For example, there will be very few jaywalkers in the Financial District near 3a.m., while there will be quite a few more during lunchtime.
